Comparative study of requantization of time-dependent mean-field for pairing dynamics

### 2017-12-06 draft1.2.tex
Modified 4.C

The obtained wave functions in the SPA and the CQ can be decomposed in the
$2n$-particle-$2n$-hole components in Fig.~\ref{fig:N50_occ}.
In the SPA, it is done as Eq. (\ref{semi_wave_func1}) and
the normalized squared coefficients $|C_m^{(E_k,J)}|^2$ are plotted
in Fig~\ref{fig:N50_occ}.
For the CQ, $|c_{k,p}^{(N)}|^2$ in Eq. (\ref{CQ_eigenstate}) are shown.
Here, $m$ and $j$ are related to each other, $2j=J-2m$.
They show excellent agreement with the exact results, not only for the
ground state but for excited states.
We find the SPA is even more precise than the CQ.
\begin{figure}[t]
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
(a1)\includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
(b1)\includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
(a2)  \includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
(b2)  \includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \caption{
Occupation probability in excited $0^+$ states
as a function of $j$ for $\Omega=50$ systems
with (a) $N=50$ and (b) $N=100$.
The upper and lower panels display the results for $x=0.5$ and $x=2$,
respectively. 
The three vertical bars at each $j$ from the left to the right represents
the squared components of the wave functions
from exact, SPA, and CQ calculations, respectively.
The left end of the horizontal axis at $j=j_{\rm min}$
corresponds to a component with $(n_1,n_2)=(N,0)$.
The next at $j=j_{\rm min}+1$ corresponds to the one with
$(n_1,n_2)=(N-2,2)$, and so on.
%From Eq. (\ref{momentum}),
%$j=-12.5$ corresponds to 0p50h configuration, $j=-11.5$ corresponds to 2p52h configuration, and so on.
}
 \label{fig:N50_occ}
\end{figure}

@@

%If the system has a deep potential at $j<0$ to prevent the wave function
%from spreading toward the region of $j<0$,
%we may justify the use of $\alpha$ as a coordinate in
%the collective model.
%The importance of the region of $j<0$ is considerable in strong pairing case.
To simulate the result of the collective model, we expand the Hamiltonian
(\ref{TDHFB_Hamiltonian_3}) up to the second order in $\phi$,
then, quantize it by $\hat{\phi}=i\partial/\partial j$ with
the ordering given by the Pauli's prescription.
The range of the coordinate $j$ is restricted to $j_{\rm min}\leq j \leq 0$
with the vanishing boundary condition $\psi(j_{\rm min})=\psi(0)=0$.
Figure~\ref{fig:Delta_E} shows two examples of the relationship 
between excitation energies and the potential energy surface.
In the panel (a), we show the case of large $\Omega$
($\Omega=50$, $N=50$, $x=2.4$),
in which
the excited $0^+$ states are bound up to second excitation.
For very large degeneracy, the pocket of energy surface is deep, 
hence the low-lying excited states may be described by $\alpha$. 
However, in the small-$\Omega$ case ($\Omega=8$, $N=16$, $x=2.4$)
of the panel (b), no excited states are bound.
This shallow pocket of potential energy is a consequence of the
choice of the collective coordinate
which represents only the $j<0$ region.
Therefore, the collective model treatment assuming
$\alpha$ ($\Delta$) as the collective coordinate
is not applicable to small-$\Omega$ and strong-pairing cases.

@@

\begin{figure}[tb]
% \begin{minipage}{0.45\hsize}
 \begin{center}
(a)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N50Xeq2p4gap_E.eps}
% \end{center}
% \end{minipage}
% \begin{minipage}{0.45\hsize}
% \begin{center}
(b)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N16Xeq2p4gap_E.eps}
 \end{center}
%\end{minipage}
\caption{Potential energy surface as functions of $\alpha$ with $x=2.4$;
(a) $\Omega=N=50$,
(b) $2\Omega=N=16$.
Horizontal (green) lines indicate
 energy spectra obtained with the CQ method
(Sec.~\ref{sec:canonical}).
%Left panels: $\Omega=50$, $N=50$ system;
% Right panels: $\Omega=8$, $N=16$ system.
}
 \label{fig:Delta_E}
\end{figure}

>>>>

The obtained wave functions in the SPA and the CQ can be decomposed in the
$2n$-particle-$2n$-hole components in Fig.~\ref{fig:N50_occ}.
In the SPA, it is done as Eq. (\ref{semi_wave_func1}) and
the normalized squared coefficients $|C_m^{(E_k,J)}|^2$ are plotted
in Fig~\ref{fig:N50_occ}.
For the CQ, $|c_{k,j}^{(N)}|^2$ in Eq. (\ref{CQ_eigenstate}) are shown.
Here, $m$ and $j$ are related to each other, $2j=J-2m$.
They show excellent agreement with the exact results, not only for the
ground state but for excited states.
We find the SPA is even more precise than the CQ.
\begin{figure}[t]
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
(a1)\includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq0p5occ_wo_adiabatic.eps}
(b1)\includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq0p5occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
%  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
(a2)  \includegraphics[height=0.45\textwidth,angle=-90]{images/N50Xeq2occ_wo_adiabatic.eps}
(b2)  \includegraphics[height=0.45\textwidth,angle=-90]{images/N100Xeq2occ_wo_adiabatic.eps}
 \end{center}
 \end{minipage}
 \caption{
Occupation probability in excited $0^+$ states
as a function of $j$ for $\Omega=50$ systems
with (a) $N=50$ and (b) $N=100$.
The upper and lower panels display the results for $x=0.5$ and $x=2$,
respectively. 
The three vertical bars at each $j$ from the left to the right represents
the squared components of the wave functions
from exact, SPA, and CQ calculations, respectively.
The left end of the horizontal axis at $j=j_{\rm min}$
corresponds to a component with $(n_1,n_2)=(N,0)$.
The next at $j=j_{\rm min}+1$ corresponds to the one with
$(n_1,n_2)=(N-2,2)$, and so on.
%From Eq. (\ref{momentum}),
%$j=-12.5$ corresponds to 0p50h configuration, $j=-11.5$ corresponds to 2p52h configuration, and so on.
}
 \label{fig:N50_occ}
\end{figure}

@@

%If the system has a deep potential at $j<0$ to prevent the wave function
%from spreading toward the region of $j<0$,
%we may justify the use of $\alpha$ as a coordinate in
%the collective model.
%The importance of the region of $j<0$ is considerable in strong pairing case.
To simulate the result of the collective model, we expand the Hamiltonian
(\ref{TDHFB_Hamiltonian_3}) up to the second order in $\phi$,
then, quantize it by $\hat{\phi}=i\partial/\partial j$ with
the ordering given by the Pauli's prescription.
The range of the coordinate $j$ is restricted to $j_{\rm min}\leq j \leq 0$
with the vanishing boundary condition $\psi(j_{\rm min})=\psi(0)=0$.
Figure~\ref{fig:Delta_E} shows two examples of the relationship 
between excitation energies and the potential energy surface.
In the panel (a), we show the case of large $\Omega$
($\Omega=50$, $N=50$, $x=2.4$),
in which
the excited $0^+$ states are bound up to second excitation.
From the collective model, the energies of ground state and first excited state are
well described, while the deviation of the energies from second excitation
becomes larger and larger.
For very large degeneracy, the pocket of energy surface is deep, 
hence the low-lying excited states may be described by $\alpha$. 
However, in the small-$\Omega$ case ($\Omega=8$, $N=16$, $x=2.4$)
of the panel (b), no excited states are bound.
We can see the excited $0^+$ states from collective model 
are not described correctly.
This shallow pocket of potential energy is a consequence of the
choice of the collective coordinate
which represents only the $j<0$ region.
Therefore, the collective model treatment assuming
$\alpha$ ($\Delta$) as the collective coordinate
is not applicable to small-$\Omega$ and strong-pairing cases.

@@

\begin{figure}[tb]
% \begin{minipage}{0.45\hsize}
 \begin{center}
(a)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N50Xeq2p4gap_E(2).eps}
% \end{center}
% \end{minipage}
% \begin{minipage}{0.45\hsize}
% \begin{center}
(b)  \includegraphics[height=0.46\textwidth,angle=-90]{images/N16Xeq2p4gap_E(2).eps}
 \end{center}
%\end{minipage}
\caption{Potential energy surface as functions of $\alpha$ with $x=2.4$;
(a) $\Omega=N=50$,
(b) $2\Omega=N=16$.
Horizontal lines 
indicate energy spectra. Black lines are obtained
from the potential energy surface, and green lines are 
obtained with the CQ method
(Sec.~\ref{sec:canonical}).
%Left panels: $\Omega=50$, $N=50$ system;
% Right panels: $\Omega=8$, $N=16$ system.
}
 \label{fig:Delta_E}
\end{figure}
